The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-16 paper.qmd
fix define uncertainty thing

From entertainment choices to news articles to insurance plans, the modern citizen is so inundated with information in every aspect of their life it can be overwhelming. 
In the face of this overflow of information, tools that effectively reduce piles of information to simple and clear ideas become more valuable. 
Even more so if they can this information with a healthy amount of scepticism.

@@

"Uncertainty visualisation" is a relatively new field in research. 
Early papers that specifically reference uncertainty visualisation appear in the late 80s [@Ibrekk1987], with geospatial information visualisation literature in the early 90s declaring this to be essential aspect of information display [@MacEachren1992; @Carr1992]. 
@fig-ibrekk depicts an example of the uncertainty visualisations discussed in these early papers. 
Despite the new terminology visualisation of uncertainty has been present since the earliest times. 
For example, box plots and histograms display variation which becomes synonymous with uncertainty when we are using them to depict the variation of an estimate. 
Today, there are an abundance of publications on the topic which makes it timely to construct a review of the field.
That is, now that there is an overwhelming amount of information, it is valuable to distil it into simple facts. 
In fact, there have already been several reviews published but a central piece of discussion is missing.

>>>>

From entertainment choices to news articles to insurance plans, the modern citizen is so inundated with information in every aspect of their life it can be overwhelming. 
In the face of this overflow of information, tools that effectively reduce piles of information to simple and clear ideas become more valuable. 
That is, we need tools that can sort the signal from the noise.

@@

"Uncertainty visualisation" is a relatively new field in research. 
Early mentions of uncertainty visualisation start to appear in the late 1980s [@Ibrekk1987], with geospatial information visualisation literature from the early 1990s declaring this to be essential aspect of any information display [@MacEachren1992; @Carr1992]. 
@fig-ibrekk depicts an example of the uncertainty visualisations discussed in these early papers. 
Despite kicking off the field, these papers did not define uncertainty visualisation.
This has led to a lack of consensus on what it means for a graphic to visualise uncertainty, an issue we will return to later.
Therefore, while the field is considered to be quite new, many of the graphics used for uncertainty visualisation have been around for much longer. 
For example, box plots and histograms display variation which becomes synonymous with uncertainty when we are using them to depict the variation of an estimate. 
Today, there are an abundance of publications on the topic which makes it timely to construct a review of the field.
That is, now that there is an overwhelming amount of information, it is valuable to distil it into simple facts. 
In fact, there have already been several reviews published but a central piece of discussion is missing.
